### 2013-09-22 phd/menger.tex
added alg top result, working on meager-nwd game

>>>>

  \centerline{Filling Games}

  \begin{definition}
    The \textbf{filling game} $\fillgame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$. In round $n+1$, player $M$ chooses $M_{n+1}$ where $M_n\subseteq M_{n+1}\in\<J\>$, and player $N$ replies with $N_{n+1}\in J$. Player $N$ wins the game if $\bigcup_{n<\omega} N_n \supseteq \bigcup_{n<\omega} M_n$. (The sets in $J$ and $\<J\>$ are thought of as nowhere-dense and meager sets, respectively.)

    The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$.
  \end{definition}

  \begin{theorem}
    $F\ktactwin{2}\sfillgame{J} \Rightarrow F\kmarkwin{2}\fillgame{J}$
  \end{theorem}

  \begin{proof}
    Enumerate the sets in $J$ as $A_\alpha$ for $\alpha<|J|$. For $M\in \<J\>$ and $n<\omega$, let $M+0=M$ and $M+n+1$ be the union of $M+n$ and the least $A_\alpha$ not contained in $M+n$.

    Let $\sigma$ be a winning $2$-tactical strategy for $N$ in $\sfillgame{\kappa}$, and assume $\sigma(M)\cup\sigma(M')\subseteq\sigma(M,M')$.

    We define a $2$-Markov strategy $\tau$ for $F$ in $\fillgame{\kappa}$ as follows:

      \[
        \tau(M_0,0) = \sigma(M_0)
      \]
      \[
        \tau(M_{n},M_{n+1},n+1) = \left\{
          \begin{array}{ll}
            \sigma(M_{n},M_{n+1}) & \text{if } M_n\subsetneq M_{n+1} \\
            \bigcup_{m\leq n}\sigma(M_n+m,M_{n+1}+m+1) & \text{otherwise}
          \end{array}
        \right.
      \]

    Let $M_0 \subseteq M_1 \subseteq \dots$ be an attack by $C$ against $\tau$. There are two possible cases:

      \begin{itemize}
        \item
          Assume $M_n=M_N$ for all $n\geq N$.

          The collection produced by $\sigma$ versus the attack
            \[
              M_N+0 \subsetneq M_N+1 \subsetneq \dots
            \] 
          must cover $M_N$ as $\sigma$ is a winning strategy.

          Let $x \in M_N$. If $x\in\sigma(M_N+0)$, then $x$ will be covered in round $N+1$ by 
            \[
              \tau(M_N,M_N,N+1)
              \supseteq \sigma(M_N+0,M_N+1)
              \supseteq \sigma(M_N+0)
            \]

          Otherwise, $x\in\sigma(M_N+n,M_N+n+1)$, and $x$ will be covered in round $N+n+1$ by 
            \[
              \tau(M_N,M_N,N+n+1)
              \supseteq \sigma(M_N+n,M_N+n+1)
            \]

        \item
          Otherwise we may find $0<f(0)<f(1)<\dots$ such that $M_{f(n)}\subsetneq M_{f(n)+1}=M_{f(n+1)}$.

          Then the collection produced by $\sigma$ versus the attack 
            \[
              M_{f(0)}\subsetneq M_{f(1)} \subsetneq M_{f(2)} \dots
            \]
          must cover $\bigcup_{n<\omega}M_n$ as $\sigma$ is a winning strategy.

          Let $x \in \bigcup_{n<\omega}M_n$. If $x\in\sigma(M_{f(0)})$, then $x$ will be covered by $\tau$ in round $f(0)+1$ by
            \[
              \tau(M_{f(0)},M_{f(0)+1},f(0)+1)
              = \sigma(M_{f(0)},M_{f(0)+1})
              \supseteq \sigma(M_{f(0)})
            \]

          Otherwise, $x\in\sigma(M_{f(n)},M_{f(n+1)})$, and $x$ will be covered by $\tau$ in round $f(n)+1$ by
            \[
              \tau(M_{f(n)},M_{f(n)+1},f(n)+1)
              = \sigma(M_{f(n)},M_{f(n)+1})
              = \sigma(M_{f(n)},M_{f(n+1)})
            \]
      \end{itemize}

      Thus $\tau$ is a winning strategy.
  \end{proof}

  \centerline{Rothberger}
